Multi-Index and Multi-Level Monte Carlo Evaluation of HJM Models

### 2016-05-07 tests/HJM/manuscript.tex
new n_f underlying plot

As for the time discretisation error, we are concerned with a rectangle quadrature
error, giving us weak and strong error rate of $1$ and $2$ respectively. Empirical
test of these rates is presented in figure \ref{img:rateFig2}.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr2.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr2.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig2} Weak (left) and strong (right) error
    for the temporal discretisation
    $\nnorm{F_{2N_t-1,N_f}-F_{N_t,N_f}}{}$. $N_f= 2^4$.}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr3.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr3.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$.}
\end{figure}

>>>>

As for the time discretisation error, we are concerned with a rectangle quadrature
error, giving us weak and strong error rate of $1$ and $2$ respectively. Empirical
test of these rates is presented in figure \ref{img:rateFig3}.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr3.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr3.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for the temporal discretisation
    $\nnorm{F_{2N_t-1,N_f}-F_{N_t,N_f}}{}$
    along with $N_t^{-1}$ and $N_t^{-2}$ reference lines in red. $N_f= 2^4$.}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr2.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr2.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$.}
\end{figure}
